%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Summer Technology Analyst} % Job title
    {Goldman Sachs \& Co\. } % Organization
    {New York, NY} % Location
    {May - August 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item   { Performed data analysis to automate strategic risk assessment of Securities technology.}
        \item { Transformed subjective risk assessments into quantitative insights by conducting PCA, K-means and HCS clustering on a self-built relational model of the firm's technology deployments and business units.
        }
        \item {Incoming algorithmic trading and quantitative finance intern for the Securities Division in Summer 2019. }
      \end{cvitems}
    }
  
  \cventry
    {Operations Research Consultant} % Job title
    {Whiting School of Engineering} % Organization
    {Baltimore, MD} % Location
    {January 2018 - PRESENT} % Date(s)
    {
      \begin{cvitems} 
        \item { Created season schedules used by entire MiLB leagues. Met challenging client demands from 14+ baseball teams and league officials, through combinatorial optimization. }
        \item { Achieved robust solutions 30\% more optimal than hand-drawn schedules, in a fraction of the time. Utilized supercomputing resources, integer programming, and cutting-edge optimization algorithms.}
      \end{cvitems}
    }
   
  \cventry
    {Teaching Assistant} % Job title
    {Department of Applied Mathematics \& Statistics} % Organization
    {Baltimore, MD} % Location
    {August 2017 - PRESENT} % Date(s)
    {
      \begin{cvitems} 
        \item { Spend 10+ hours/week teaching section of 25+ students, as well as 1-1 tutoring and mentorship.}
        \item {Classes taught include Intro to Optimization and Discrete Mathematics.}
      \end{cvitems}
    }
  
%---------------------------------------------------------
\end{cventries}